% LaTeX resume using res.cls
\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\lhead{\hspace*{-\sectionwidth}Youzheng Chen} % force lhead all the way left
\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the document

\begin{document} 

\thispagestyle{empty}
\name{YOUZHENG CHEN\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name      

\address{
Beijing Univ. Post. \& Telecom. \\
No.10 Xitucheng Road, Haidian, Beijing \\
100876 China
}
\address{
Tel: +86-152-1083-4006 \\
Email: youzhengc@gmail.com \\
URL: http://cloudzfy.github.io
}
                                  
\begin{resume}         
\vspace{0.1in}
\section{EDUCATION} 
\vspace{0.1in}          
{\bf Beijing University of Posts and Telecommunications, China}\hfill {\em June 2013} \\[3pt]
Bachelor of Engineering in Software Engineering \\[3pt]
GPA: 3.60/4.00(overall) 3.82/4.00(major)  

 
\section{PROJECTS AND RESEARCH EXPERIENCES}
\vspace{-0.05in}
\begin{tabbing}
\hspace{4.7in}\= \kill
{\bf JAIN SLEE Access Control System \& Call Center}     \>{\em Nov. 2012 - Present} \\
\end{tabbing}\vspace{-20pt}
\begin{itemize}
\item[] Project Website: http://cloudzfy.github.io/gryffin-as
\item[] Designed IMS Media Resource Controller for Interactive Voice Response (IVR) function
\item[] Designed and implemented MRCPv2 Resource Adaptor of JAIN SLEE Framework
\item[] Integrated JVoiceXML to enhance extensibility of Media Resource Controller
\end{itemize}

\begin{tabbing}
\hspace{3.4in}\= \hspace{1.3in}\= \kill
{\bf AtMars Microblog Open Source Project} \>Team Leader \> {\em July 2012 - Aug. 2012}\\
\end{tabbing}\vspace{-20pt}
\begin{itemize}
\item[] Project Website: http://cloudzfy.github.io/atmars
\item[] Designed the architecture of AtMars Microblog in Struts + Spring + Hibernate (SSH) Framework
\item[] Designed user interface of AtMars in HTML5, Javascript and CSS3
\end{itemize}

\begin{tabbing}
\hspace{3.4in}\= \hspace{1.3in}\= \kill
{\bf ECHelper Mobile Health System} \>Team Leader \> {\em Jan. 2012 - Apr. 2012}\\
\end{tabbing}\vspace{-20pt}
\begin{itemize}
\item[] Project Website: http://cloudzfy.github.io/echelper
\item[] Designed the architecture of ECHelper with multiple Microsoft Technology (Windows Azure, Windows 8, Windows Phone 7, etc)
\item[] Designed hareware driver for ECG sensor to record patient data
\end{itemize}

\begin{tabbing}
\hspace{3.4in}\= \hspace{1.3in}\= \kill
{\bf Kinect sports director} \>Team Leader \> {\em Sept. 2011 - Jan. 2012}\\
\end{tabbing}\vspace{-20pt}
\begin{itemize}
\item[] Designed WPF Application to recognize body skeleton by Microsoft Kinect SDK
\item[] Designed algorithm for measuring the differences between userÕs actions and standard actions
\end{itemize}

\begin{tabbing}
\hspace{3.4in}\= \hspace{1.3in}\= \kill
{\bf Doubango-based IMS UE for Teaching Cases} \>Team Leader \> {\em Nov. 2011 - May 2012}\\
\end{tabbing}\vspace{-20pt}
\begin{itemize}
\item[] Project Website: http://cloudzfy.github.io/myboghe
\item[] Designed and implemented the IMS client and IMS server for Private Chat, Public Chat and Presence Service
\item[] Designed the teaching experiments for three weeks on Doubango-based IMS UE in a simplified model
\end{itemize}

\begin{tabbing}
\hspace{3.4in}\= \hspace{1.3in}\= \kill
{\bf SIP Communication Simulation in QualNet} \>Team Leader \> {\em Oct. 2010 - June 2011}\\
\end{tabbing}\vspace{-20pt}
\begin{itemize}
\item[] Used simulation platform QualNet produced by SCALABLE Network Technologies
\item[] Simulated Proxy routed SIP-based VoIP in different domains
\item[] Analyzed and designed QualNet components for SIP simplified model
\end{itemize}


\section{PUBLICATIONS}
\vspace{0.1in}
``Research and Implementation of an IMS-based AS/MRFC Model for IVR Services", {\bf Youzheng Chen}, Baozhong Cheng, and Xiaoyan Zhang, {\em Communications Workshops (ICC), 2014 IEEE International Conference on} (under review)

``Development of Doubango-based IMS UE for Teaching Experiments", {\bf Youzheng Chen}, Baozhong Cheng, Xiaoyan Zhang, Yi Sun, Jin Xie, and Kun Li, {\em IT Convergence and Security (ICITCS), 2013 International Conference on}, 2013, pp. 319-322

``Analysis and Design of IMS Services on IMS AS for Teaching Experiments", Kun Li, Baozhong Cheng, Xiaoyan Zhang, {\bf Youzheng Chen}, Yi Sun, and Jin Xie, {\em Information Technology and Electronic Commerce (ICITEC), 2013 1st International Conference on}, 2013, pp. 72-75

 
 
\section{HONORS AND AWARDS}
\vspace{-0.05in}
\begin{tabbing}
\hspace{5.4in}\= \kill
Scholarship in the People's Daily Online 2012 (Top 1.01\%) \>{\em Oct. 2012} \\[7pt]
Third Prize in the Software Design Challenge of Microsoft Imagine Cup 2012 (Top 0.13\%) \\ \> {\em Apr. 2012} \\[7pt]
Silver Award of the Sixth ACM-ICPC School Contest of BUPT (Top 2.47\%) \> {\em Mar. 2012} \\[7pt]
Honorable Mentions in the 2012 Mathematical Contest in Modeling \> {\em Feb. 2012} \\[7pt]
Second Prize in the 2011 China-Pub Cup Global Mathematical Modeling Certificate Contest \\ \> {\em May 2011} \\[7pt]
Second-class Scholarship, Beijing University of Posts and Telecommunications \> {\em Nov. 2011} \\[7pt]
Third-class Scholarship, Beijing University of Posts and Telecommunications \> {\em Nov. 2010} \\[7pt]
Second Prize in the Chinese Mathematical Olympiad in Senior \> {\em Oct. 2008} \\[7pt]
First prize in the National Mathematical Contest for Junior High School Students (Top 2.81\%) \\ \> {\em Apr. 2006}
\end{tabbing}

\section{PROGRAMMING SKILLS}
C, C++, C\#, Java, JavaScript, \LaTeX, Unix Shell Script

\end{resume}
\end{document}