\documentclass[margin]{res}
\usepackage{enumitem}
%\textwidth=5.2in
\begin{document}

\thispagestyle{empty}
\name{Youzheng Chen\\[12pt]}

\begin{resume}
\section{EDUCATION}
{\bf University of Southern California}\hfill Los Angeles, CA \\
Master of Science in Computer Science \hfill {\em Aug. 2014 - Present} \\[8pt]
{\bf Beijing University of Posts and Telecommunications}\hfill Beijing, China \\
Bachelor of Engineering in Software Engineering \hfill {\em Sept. 2009 - Jun. 2013}
 
\section{WORK EXPERIENCE}
{\bf University of Southern California} \hfill  Los Angeles, CA \\[2pt]
{\em Research Assistant} (Directed by Prof. Michael Arbib) \hfill {\em June. 2015 - Present} \\[-8pt]
\begin{itemize}[topsep=-1pt,parsep=1pt]
\item Analyzed the effect of different basal ganglia pathways in brain function
\item Designed and Implemented associative learning model through time
\end{itemize}

{\bf Beijing University of Posts and Telecommunications} \hfill Beijing, China \\[2pt]
{\em Research Assistant} (Directed by Prof. Baozhong Cheng) \hfill {\em Nov. 2010 - June 2014} \\[-8pt]
\begin{itemize}[topsep=-1pt,parsep=1pt]
\item Lead and Implemented Doubango-based IMS UE for teaching cases
\item Designed access control system and call center based on JAIN SLEE architecture
\end{itemize}

\section{RESEARCH EXPERIENCE}
{\bf University of Southern California} \hfill Los Angeles, CA \\[8pt]
{\em MNS-based Neuron Coding on Action and Inaction} \hfill {\em June 2015 - Present} \\[-8pt]
\begin{itemize}[topsep=-1pt,parsep=1pt]
\item Analyzed the influence of hyperdirect and indirect pathway on Inaction case
\item Designed reinforcement learning rules on associative learning through time
\item Designed basal ganglia model based on Nengo Library
\end{itemize}

{\em Deep Learning Model on Rainfall Estimation} \hfill {\em Oct. 2015 - Dec. 2015} \\[-8pt]
\begin{itemize}[topsep=-1pt,parsep=1pt]
\item Designed deep learning model based on Marshall-Palmer equation
\item Implemented layers and nets in neural network based on Caffe Library
\item Analyzed model performance and predicted rainfall value in Kaggle competition
\end{itemize}

{\em Reinforcement-Learning-based Basal Ganglia Model} \hfill {\em Feb. 2015 - May 2015} \\[-8pt]
\begin{itemize}[topsep=-1pt,parsep=1pt]
\item Integrated and analyzed the role of the indirect pathway of the basal ganglia
\item Analyzed reinforcement learning effect under dopamine depletion
\item Applied reinforcement learning rule on the weights of cortico-striatal connections
\item Documented relative publications in the Brain Operational Database System
\end{itemize}

{\em SL Real-Time Simulation on NAO Robot} \hfill {\em Apr. 2015 - May 2015} \\[-8pt]
\begin{itemize}[topsep=-1pt,parsep=1pt]
\item Implemented inverse kinematics algorithm on the control of the COG
\item Implemented direct kinematics algorithm on the control of robot leg action
\item Analyzed feedback system using PID control
\end{itemize}

{\em Analysis of GPU Virtualization on Cloud Computing} \hfill {\em Oct. 2014 - Nov. 2014} \\[-8pt]
\begin{itemize}[topsep=-1pt,parsep=1pt]
\item Analyzed virtualization approaches in modern operating systems
\item Compared the design of GPU virtualization among VMWare, Xen, etc.
\item Evaluated the potential research direction on Gaming as a Service (GaaS)
\end{itemize}

{\bf Beijing University of Posts and Telecommunications} \hfill Beijing, China \\[8pt]
{\em JAIN SLEE Access Control System \& Call Center} \hfill {\em Nov. 2012 - June 2014} \\[-8pt]
\begin{itemize}[topsep=-1pt,parsep=0pt]
\item Developed IMS Media Resource Controller for Interactive Voice Response (IVR)
\item Analyzed and Remodeled MRCPv2 Resource Adaptor of JAIN SLEE
\item Assembled JVoiceXML and enhanced extensibility of Media Resource Controller
\end{itemize}

{\em ECHelper Mobile Health System} \hfill {\em Jan. 2012 - Apr. 2012} \\[-8pt]
\begin{itemize}[topsep=-1pt,parsep=1pt]
\item Devised the architecture with Windows Azure, Windows 8, etc
\item Programmed hardware driver for ECG sensor to record patient data
\end{itemize}

{\em Doubango-based IMS UE for Teaching Cases} \hfill {\em Nov. 2011 - May 2012} \\[-8pt]
\begin{itemize}[topsep=-1pt,parsep=1pt]
\item Simplified IMS client and IMS server for Chat Room and Presence Service
\item Developed three-week IMS UE teaching experiments
\end{itemize}

\section{PUBLICATIONS}
``Research and Implementation of an IMS-based AS/MRFC Model for IVR Services", {\bf Youzheng Chen}, Baozhong Cheng, and Xiaoyan Zhang, {\em IT Convergence and Security (ICITCS), 2014 International Conference on}, 2014, pp. 1-5

``Development of Doubango-based IMS UE for Teaching Experiments", {\bf Youzheng Chen}, Baozhong Cheng, Xiaoyan Zhang, Yi Sun, Jin Xie, and Kun Li, {\em IT Convergence and Security (ICITCS), 2013 International Conference on}, 2013, pp. 319-322

``Analysis and Design of IMS Services on IMS AS for Teaching Experiments", Kun Li, Baozhong Cheng, Xiaoyan Zhang, {\bf Youzheng Chen}, Yi Sun, and Jin Xie, {\em Information Technology and Electronic Commerce (ICITEC), 2013 1st International Conference on}, 2013, pp. 72-75

\section{AWARDS}
\vspace{-0.05in}
\begin{tabbing}
\hspace{4.7in}\= \kill
Scholarship in the People's Daily Online 2012  \>{\em Oct. 2012} \\[7pt]
Third Prize in the Software Design Challenge of Microsoft Imagine Cup 2012 \\ \> {\em Apr. 2012} \\[7pt]
Silver Award of the Sixth ACM-ICPC School Contest of BUPT \> {\em Mar. 2012} \\[7pt]
Honorable Mentions in the 2012 Mathematical Contest in Modeling \> {\em Feb. 2012} \\[7pt]
Second-class Scholarship, Beijing University of Posts and Telecomm. \> {\em Nov. 2011} \\[7pt]
Third-class Scholarship, Beijing University of Posts and Telecomm. \> {\em Nov. 2010} \\[7pt]
Second Prize in the Chinese Mathematical Olympiad in Senior \> {\em Oct. 2008} \\[7pt]
First prize in the National Mathematical Contest for Junior High School Students \\ \> {\em Apr. 2006}
\end{tabbing}

\section{SKILLS}
C, C++, C\#, Java, Matlab, \LaTeX, Unix Shell Script

\end{resume}
\end{document}